Open-source tools in R for landscape ecology

### 2021-02-08 paper/paper.Rmd
Not sure what is going on...
...
Funding

No funding was received by the authors for this research and publication.

>>>>

LJG was supported by the Natural Environment Research Council (NERC) grant *A complex-systems approach to improve understanding of the biodiversity-landscape structure relationship*, grant number NE/T009373/1. 
All other authors did not receive any funding for this research.

### 2021-02-08 paper/paper.tex
Not sure what is going on...
...
Funding

No funding was received by the authors for this research and publication.

>>>>

LJG was supported by the Natural Environment Research Council (NERC) grant \emph{A complex-systems approach to improve understanding of the biodiversity-landscape structure relationship}, grant number NE/T009373/1.
All other authors did not receive any funding for this research.
